---
title: Technical Specifications Document 
subtitle: | 
  Southern Atlantic Albacore MSE 
author: 
  - name: Adrian Hordyk
    affiliation: Blue Matter Science Ltd
  - name: "Rodrigo Sant'Ana"
    affiliation: Universidade do Vale do Itajaí
  - name: "Bruno Mourato"
    affiliation: Universidade Federal de São Paulo
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
    toc_depth: 2
    use_bookdown: yes
urlcolor: blue
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('../Condition/LifeHistoryParameters.R')
```

# Introduction

```{r message=FALSE, warning=FALSE}

library(ggplot2)
library(ggExtra)
nsim <- 200
```

This document describes the technical details of the management strategy evaluation (MSE) framework being developed for the Southern Atlantic albacore (SALB) tuna fishery. This project is supported by the Marine Stewardship Council's [Ocean Stewardship Fund](https://www.msc.org/what-we-are-doing/our-collective-impact/ocean-stewardship-fund/impact-projects/south-atlantic-albacore-tuna-harvest-strategy-project-2025) with a multi-stakeholder collaboration between ICCAT members, fisheries and NGOs.

This is a living document and will be continually updated as the project progresses.

The overall objective of this project is to develop candidate management procedures (CMPs) for the SALB fishery, test their performance across the key uncertainties in the knowledge of the fishery dynamics, and adopt the harvest strategy that has is most likely to achieve the fishery's management objectives.

The project is currently in its initial phase, with the following aims:

1.  Develop an MSE framework for SALB;
2.  Develop base case operating models (OM) with two different modelling frameworks: [Stock Synthesis 3](https://nmfs-ost.github.io/ss3-website/) (SS3) and the [Rapid Conditioning Model](https://openmse.com/tutorial-rcm/) (RCM), and compare their results;
3.  Identify the primary uncertainties in the knowledge of the fishery system;
4.  Develop an OM Grid spanning the uncertainties and condition OMs using SS3 (OM Grid Approach);
5.  Develop a single stochastic OM conditioned with RCM that spans the uncertainties included in the SS3 Grid (Stochastic OM Approach);
6.  Compare the results of the OM Grid Approach and Stochastic OM Approach and discuss the relative pros and cons of the two methodologies.

The intention of this initial phase is to demonstrate the SALB MSE framework and compare the results of the two methods for conditioning the operating models.

Currently the model uses SALB data up to 2018. It will be updated with the most recent fishery data one the demonstration MSE framework has been reviewed by representatives of the managers and stakeholders.

Similarly, the life-history parameters and other technical specifications of the model (documented below) have not been reviewed by the SCRS or other interested stakeholders, and may be revised and updated once the initial framework has been reviewed.

# Data

The operating models have been conditioned using the same data used in the most recent stock assessments [@winker2020; @matsumoto2020].

## Catch

The SALB catches have been organized into 8 fleets (Table \@ref(tab:catch-table); Figure \@ref(fig:catch-plot)).

```{r catch-table}

CatchFleetDF <- data.frame(Fleet=1:8,
                           Nations= c(
                             'Chinese Taipei (LL), Korea (LL)',
                             "China (LL), E. C. Spain (LL), E. C. Portugal (LL), Japan (LL), Philippines (LL), St Vincent and Grenadier (LL), USA (LL), Vanuatu (LL), Honduras (LL), Nei (LL), Côte D'Ivoire (LL), EU.United Kingdom (LL), Seychelles (LL), UK.Sta Helena (LL), Angola (LL), Senegal (LL), Trinidad and Tobago (LL)",
                             "Same as 2",
                             "Same as 2",
                             "Brazil (LL, SU), Panama (LL), South Africa (LL, UN), Argentina (LL, TW, UN), Belize (LL), Cambodia (LL), Cuba (LL, UN), Namibia (LL)",
                             "Brazil (BB, GN, HL, PS, TW, UN), E. C. Spain (PS), E. C. France (BB, PS), E. C. Portugal (BB, PS), Japan (BB, PS), Namibia (BB), Korea (BB) ,Maroc (PS), Panama (PS), South Africa (BB, HL, PS, RR, SP), USA (PS), USSR (SU, UN), UK St Helena (BB, RR), Chinese Taipei (GN), Nei (BB, PS), Argentina (PS), Belize (PS), Cape Verde (PS), Curaçao (PS), Guatemala (PS), Côte D'Ivoire (PS), Ghana (BB, PS), Guinea Ecuatorial (UN, HL), Guinée Rep. (PS), St. Vincent and Grenadines (PS), Guinea Ecuatorial (HL)",
                             "Same as 6",
                             "Uruguay (LL)"),
                           `Time Period`= c(
                             '1964 -- 2018',
                             '1956 -- 1969',
                             '1970 -- 1975',
                             '1976 -- 2018',
                             '1959 -- 2018',
                             '1964 -- 1998',
                             '1999 -- 2018',
                             '1981 -- 2013')
                           
                           )

knitr::kable(CatchFleetDF, caption = "The eight fleets used for the SALB catch data.", format = "html") |>
  kableExtra::kable_styling(full_width = F)

```

```{r catch-plot, fig.cap='Time series plot of the SALB catch data by fleet.', fig.height=4.5, fig.width=8}

library(ggplot2)

RCMData <- readRDS('../Condition/SALB.rcmdata')


Catch <- array2DF(RCMData@Chist, 'Catch') 
Catch$Year <- as.numeric(Catch$Year)

ggplot(Catch, aes(x=Year, y=Catch)) +
  facet_wrap(~Fleet, scales='free_y') +
  geom_line() +
  theme_bw()

```

## Indices

Three indices of abundance were used in the SALB assessment (Table \@ref(tab:index-table); Figure \@ref(fig:index-plot)).

```{r index-table}

IndexFleetDF <- data.frame(Fleet=c(1,4,8),
                           Nations= c(
                             'Chinese Taipei (LL)',
                             'Japan (LL)',
                             "Uruguay (LL)"),
                           `Time Period`= c(
                             '1967 -- 2018',
                             '1976 -- 2011',
                             '1983 -- 2011')
                           
                           )

knitr::kable(IndexFleetDF, caption = "The three indices of abundance.",
             format = "html") |>
  kableExtra::kable_styling(full_width = F)
```

```{r index-plot, fig.cap='Time series plot of the SALB index data by fleet.', warning=FALSE, fig.height=2.5, fig.width=8}

Indices <- array2DF(RCMData@Index, 'Index') 
Indices$Year <- as.numeric(Indices$Year)

Indices <- Indices |> 
  dplyr::group_by(Fleet) |>
  dplyr::mutate(Index=Index/mean(Index, na.rm=TRUE))
  

ggplot(Indices, aes(x=Year, y=Index)) +
  facet_wrap(~Fleet, scales='free_y') +
  geom_line() +
  expand_limits(y=0)+
  theme_bw()

```

## Composition Data

Catch-at-length data was aggregated using the same fleet structure used for catch (Figure \@ref(fig:cal-plot))

```{r cal-plot, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, fig.cap='Length composition data for the 8 fleets. The catch-at-length data has been summed over all years and standardized by dividing by total number of samples (n) for each fleet.'}

CAL <- array2DF(RCMData@CAL, 'CAL') 
CAL$Year <- as.numeric(CAL$Year)
CAL$Class <- as.numeric(CAL$Class)

CAL <- CAL |>
  dplyr::group_by(Fleet) |>
  dplyr::filter(is.na(CAL)==FALSE, CAL>0.01) |>
  dplyr::group_by(Fleet, Class) |>
  dplyr::summarise(CAL=sum(CAL)) |>
  dplyr::group_by(Fleet) |>
  dplyr::mutate(n=sum(CAL), CAL=CAL/n) 
  
CALn <- CAL |> dplyr::group_by(Fleet) |>
  dplyr::summarise(n=format(unique(n), big.mark=",", scientific=FALSE),
                   Class=min(Class))

ggplot(CAL) +
  facet_wrap(~Fleet, scales='free_y') +
  geom_line(linewidth=0.8, aes(x=Class, y=CAL)) +
  expand_limits(y=0)+
  geom_text(data=CALn, aes(x=-Inf, y=0.5* Inf, label=paste('n = ', n)), hjust=-0.1, vjust=1) +
  theme_bw() +
  labs(x='Length Class (cm)',
       y='Relative Number')

```

# Base Life-History Parameters

Table \@ref(tab:LH-base-case) shows the life history parameters for the Base Case operating model.

```{r LH-base-case}

LHBaseCase <- data.frame(Parameter=c(
  '$M$', 
  '$L_\\infty$',
  '$K$',
  '$t_0$',
  '$a$',
  '$b$',
  '$L_{50}$',
  '$L_{95}$',
  '$h$',
  '$\\sigma_R$'
  ),
  Description=c(
    'Natural mortality rate',
    'von Bertalanffy asymptotic length',
    'growth coefficient',
    'expected age at L=0',
    'length-weight relationship; average weight at L=1',
    'length-weight relationship exponent',
    'Length corresponding with 50% probability of maturity',
    'Length corresponding with 95% probability of maturity',
    'Steepness of Beverton-Holt SRR',
    'Standard deviation of the log-normally distributed recruitment deviations'
  ),
  Value=c(M_mu,
          Linf_mu,
          K_mu,
          t0_mu,
          as.character(signif(Wa_mu,3)),
          Wb_mu,
          L50_mu,
          L95_mu,
          h_mu,
          PE_mu),
  Reference=c('@iccat2016; @iccat2004',
              '@lee2007',
              '@lee2007',
              '@lee2007',
              '@penney1994',
              '@penney1994',
              '@travassos2024',
              '@travassos2024',
              'Assumed based on @merino2020',
              'Assumed'
              )
)

knitr::kable(LHBaseCase, caption = "Life history parameters for the Base Case Operating Model",
             format = "html",
             digits=2) |>
  kableExtra::kable_styling(full_width = T)

```

# Uncertainties in Life-History Parameters

The SALB MSE currently considers two axes of uncertainty in the life-history parameters (see [Base Life-History Parameters]):

1.  Natural mortality (*M*)
2.  Steepness of the Beverton-Holt stock-recruit relationship (*h*)

Potential additional uncertainties could include:

1.  Additional uncertainties that could be considered for the life-history parameters are:
2.  Uncertainty in the von Bertalanffy growth parameters
3.  Variation in the maturity parameters (e.g., bounded by the confidence intervals reported by @travassos2024)
4.  Variation in the recruitment deviations $(\sigma_R)$

The uncertainty in the continuous life-history parameters was deal with in two ways.

First, a discrete OM Uncertainty Grid was developed assuming three levels for each parameter. This approach follows the methodology used in other ICCAT MSE processes, and results in 9 individual operating models, each with discrete values from the factorial combinations of the axes and levels of uncertainty (Table \@ref(tab:LH-grid)).

```{r LH-grid}

Grid <- data.frame(OM=1:9,
                   M=rep(c(0.3, 0.35, 0.4),3),
                   h=rep(c(0.7, 0.8, 0.9), each=3)
)
  
knitr::kable(Grid, caption = "The values used in the discrete uncertainty grid.",
             format = "html",
             digits=2) |>
  kableExtra::kable_styling(full_width = T)

```

The second approach involved sampling `r nsim`values of the life-history parameters from a multivariate distribution, and running the OM Conditioning model (see next section) for each sample. A single OM was then generated, incorporating the output of the `r nsim` fits to the data with the stochastic life-history parameters.

The methodology for sampling the life-history parameters was based on the methodology developed by @taylor2024 for the Southern Atlantic Swordfish.

The life-history parameters were assumed to be log-normally distributed (Table \@ref(tab:LH-stochastic)), and were sampled from a multivariate distribution truncated at 1.96 standard deviations. The truncation was used to exclude extreme values from the tails of the distribution.

The covariance matrix for the multivariate distribution was generated by using the correlation between *M* and *h* reported by the FishLife package [@thorson2023] for *Thunnus alalunga.*

Figure \@ref(fig:stochastic-plot) shows a scatterplot and marginal histograms of the `r nsim` samples of the stochastic life-history parameters.

```{r LH-stochastic}

LHStochastic <- data.frame(Parameter=c(
  '$M$', 
  '$h$'
  ),
  Mean=c(M_mu,h_mu),
  SD=c(M_sd, h_sd)
)

knitr::kable(LHStochastic, caption = "The mean and standard deviation used to generate the stochastic life-history parameters.",
             format = "html",
             digits=2) |>
  kableExtra::kable_styling(full_width = T)
```

```{r stochastic-plot, fig.cap='Scatterplot with marginal histograms of the samples of the stochastic life-history parameters.', fig.height=4.5, fig.width=4.5}

Stochastic <- read.csv('../Condition/LHSamples.csv') 
  
p <- ggplot(Stochastic, aes(x=M, y=h)) +
  geom_point() +
  theme_bw()

ggExtra::ggMarginal(p, type='histogram')
```

# OM Conditioning

The Operating Models were conditioned using two different modelling frameworks: [Stock Synthesis 3](https://nmfs-ost.github.io/ss3-website/) (SS3) and the [Rapid Conditioning Model](https://openmse.com/tutorial-rcm/) (RCM).

The operating models had `r nsim` simulations and a 30-year projection period.

## Stock Synthesis 3

TBD

## Rapid Conditioning Model (RCM)

The RCM was used to condition two different OMs: *RCM* *Base Mean* and *RCM* *Base Stochastic.*

The model was run assuming a dome-shaped selectivity pattern all fleets.

```{=html}
<!--#
for the long-line fleets (LL) and dome-shaped for the purse-seine (PS) and bait boats (BB; Table \@ref(tab:selectivity-table)).  
-->
```

A minimum CV of 0.2 was assumed for all indices. The effective sample size for the length composition data was set to 50.

````{=html}
<!--#
```{r selectivity-table}

df <- CatchFleetDF
df <- df |> 
  dplyr::select(-Time.Period) |>
  dplyr::mutate(Selectivity=c('Logistic',
                               'Logistic',
                               'Logistic',
                               'Logistic',
                               'Logistic',
                               'Dome',
                               'Dome',
                               'Logistic'))

knitr::kable(df, caption = "The assumed selectivity patterns for the 8 fleets used in the RCM OM Conditioning.", format = "html") |>
  kableExtra::kable_styling(full_width = F)

```
-->
````

### RCM Base Mean

The *RCM* *Base Mean* OM was conditioned using the mean value of the stochastic life-history parameters (see Section \@ref(life-history-parameters)); i.e., all life-history parameters were identical across the individual simulations.

In this OM, the historical fishery dynamics are identical across the simulations, with stochastic recruitment deviations and observation error in the projection period.

This OM is used to compare the predictions of RCM with the output of SS3 with the same structure and assumed parameter values.

### RCM Base Stochastic

The *RCM* *Base Stochastic* OM was generated by running the RCM `r nsim` times (each simulation) and randomly sampling the stochastic life-history parameters (see Section \@ref(uncertainties-in-life-history-parameters)).

In this OM, there are `r nsim` predictions of the historical fishery dynamics; i.e., a single OM that includes the stochastic variability in the life-history parameters.

# Historical Fishery Dynamics

> This section will be updated with a comparison of the output of both the SS3 and RCM OMs.

Figure \@ref(fig:rcm-hist) shows the time series plots of the estimated SB/SBMSY for the RCM Base Mean and RCM Base Stochastic OMs.

```{r rcm-hist, fig.cap='Time series plots of the estimated SB/SBMSY for the RCM Base Mean and RCM Base Stochastic OMs.', fig.height=4.5, fig.width=8}

OM_Mean <- readRDS('../OM/RCM_Mean.om')
Hist_Mean <- readRDS('../Hist/RCM_Mean.hist')
Hist_Stochastic <- readRDS('../Hist/RCM_Stochastic.hist')


HistYears <- seq(OM_Mean@CurrentYr, by=-1, length.out=OM_Mean@nyears) |> rev()

SB_SBMSY_Mean <- apply(Hist_Mean@TSdata$SBiomass, 1:2, sum)/matrix(Hist_Mean@Ref$ReferencePoints$SSBMSY, OM_Mean@nsim, OM_Mean@nyears, byrow=FALSE)
dimnames(SB_SBMSY_Mean) <- list(Sim=1:OM_Mean@nsim,
                                Year=HistYears)
SB_SBMSY_Stochastic <- apply(Hist_Stochastic@TSdata$SBiomass, 1:2, sum)/matrix(Hist_Stochastic@Ref$ReferencePoints$SSBMSY, OM_Mean@nsim, OM_Mean@nyears, byrow=FALSE)

dimnames(SB_SBMSY_Stochastic) <- list(Sim=1:OM_Mean@nsim,
                                Year=HistYears)


SB_SBMSY_Mean <- array2DF(SB_SBMSY_Mean)
SB_SBMSY_Mean$Year <- as.numeric(SB_SBMSY_Mean$Year)
SB_SBMSY_Mean$Value <- as.numeric(SB_SBMSY_Mean$Value)
SB_SBMSY_Mean$Model <- 'Mean'

SB_SBMSY_Stochastic <- array2DF(SB_SBMSY_Stochastic)
SB_SBMSY_Stochastic$Year <- as.numeric(SB_SBMSY_Stochastic$Year)
SB_SBMSY_Stochastic$Value <- as.numeric(SB_SBMSY_Stochastic$Value)
SB_SBMSY_Stochastic$Model <- 'Stochastic'

df <- dplyr::bind_rows(SB_SBMSY_Mean, SB_SBMSY_Stochastic)


ggplot(df, aes(x=Year, y=Value, group=Sim)) +
  facet_wrap(~Model) +
  geom_line() +
  expand_limits(y=0) +
  labs(y='SB/SBMSY') +
  geom_hline(yintercept =1, linetype=2) +
  theme_bw()
```

## Comparision of Base Mean OMs

> Compare Base Mean SS3 and RCM output

## Comparison of Base Stochastic OMs

> Compare Base Stochastic SS3 and RCM output

# References
